Multispecies survey specifications

### 2020-11-05 msSurveysTest.Rmd
add prelim comparison plots

Crunch a few things to get true age comps
```{r}
# age classes
totNagecl <- omlist_ss$truenums_ss %>%
  group_by(species, agecl, time) %>%
  summarize(numAtAge = sum(atoutput))

@@

@@

# plot length frequencies by timestep (one species)
plotlen <- function(dat, truedat=NULL){

    ggplot(dat, aes(upper.bins)) +
    geom_bar(aes(weight = atoutput)) +
    theme_tufte() +
    xlab("length (cm)") +
    ylab("number") +
    labs(subtitle = paste(scenario.name,
                          dat$species)) +
    facet_wrap(~time, ncol=6, scales="free_y")

@@

# plot numbers at age by timestep (one species)
Natageplot <- function(dat, effN=1, truedat=NULL){
  ggplot() +
    geom_point(data=dat, aes(x=agecl, y=atoutput/effN, color="Est Comp")) +
    {if(!is.null(truedat)) geom_line(data=dat, aes(x=agecl, y=numAtAge/totN, color="True Comp"))} + 
    theme_tufte() +
    theme(legend.position = "bottom") +    
    xlab("age/agecl") +
    ylab("number") +
    labs(subtitle = paste(scenario.name,
                          dat$species)) + 
    facet_wrap(~time, ncol=6, scales="free_y")
}

@@

```{r read-newsurvs}

@@

@@

catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name, "fishCatch.rds")))
catchbio_ss <- catchbio_ss[[1]] #in same time unit as surveys

fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

@@

fish_len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsLenComp.rds")))

@@

fishwtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsWtAtAge.rds")))
fishwtage <- fishwtage[[1]] #need to change time units?

fish_annage_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullAgeComp.rds")))
fish_annage_comp <- fish_annage_comp[[1]]

@@

fish_annage_wtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullWtAtAge.rds")))
fish_annage_wtage <- fish_annage_wtage[[1]] #need to change time units?

@@

### Visualize surveys with different q and selectivity {.tabset #census}

@@

@@

@@

@@

@@

>>>>

Crunch a few things to get true age comps and census length comp for later
```{r}
# age classes
totNagecl <- omlist_ss$truenums_ss %>%
  group_by(species, agecl, time) %>%
  summarize(numAtAge = sum(atoutput))

@@

# census length comps each survey
lf_census_prop <- list()
for(s in names(len_comp_data)){
  lcomp <- as.data.frame(len_comp_data[[s]][[1]])
  lf_census_tot <- aggregate(lcomp$atoutput,list(lcomp$species, lcomp$time),sum )
  names(lf_census_tot) <- c("species", "time","totlen")
  lf_census <- left_join(lcomp, lf_census_tot) %>%
    rename(censuslen = atoutput)
  lf_census_prop[[s]] <- lf_census
}

# fishery length comps (haven't changed here)

@@

# plot length frequencies by timestep (one species)
plotlen <- function(dat, effN=1, truedat=NULL){

    ggplot(mapping=aes(x=upper.bins)) +
    {if(!is.null(truedat)) geom_bar(data=truedat, aes(weight = censuslen/totlen), fill="Census Len Comp", alpha = 5/10)} +
    geom_bar(data=dat, aes(weight = atoutput/effN), fill="Len Comp") +
    theme_tufte() +
    xlab("length (cm)") +
    {if(is.null(truedat)) ylab("number")} +
    {if(!is.null(truedat)) ylab("proportion")} +
    labs(subtitle = paste(scenario.name,
                          dat$species)) +
    facet_wrap(~time, ncol=6, scales="free_y")

@@

# plot numbers at age by timestep (one species)
Natageplot <- function(dat, effN=1, truedat=NULL){
  ggplot() +
    geom_point(data=dat, aes(x=agecl, y=atoutput/effN, color="Est Comp")) +
    {if(!is.null(truedat)) geom_line(data=dat, aes(x=agecl, y=numAtAge/totN, color="True Comp"))} + 
    theme_tufte() +
    theme(legend.position = "bottom") +    
    xlab("age/agecl") +
    {if(is.null(truedat)) ylab("number")} +
    {if(!is.null(truedat)) ylab("proportion")} +
    labs(subtitle = paste(scenario.name,
                          dat$species)) + 
    facet_wrap(~time, ncol=6, scales="free_y")
}

@@

```{r read-newsurvs, message=FALSE, warning=FALSE}

@@

source(here("config/mssurvey_spring_01.R"))
source(here("config/msfishery_01.R"))

@@

catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishCatch.rds")))
catchbio_ss <- catchbio_ss[[1]] #in same time unit as surveys

fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

@@

fish_len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishObsLenComp.rds")))

@@

fishwtage <- readRDS(file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishObsWtAtAge.rds")))
fishwtage <- fishwtage[[1]] #need to change time units?

fish_annage_comp <- readRDS(file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishObsFullAgeComp.rds")))
fish_annage_comp <- fish_annage_comp[[1]]

@@

fish_annage_wtage <- readRDS(file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishObsFullWtAtAge.rds")))
fish_annage_wtage <- fish_annage_wtage[[1]] #need to change time units?

@@

### Visualize surveys with different q and selectivity {.tabset #survey}

@@

for(s in names(len_comp_data)){
  cat("  \n##### ",  s,"  \n")
  lcompsub <- as.data.frame(len_comp_data[[s]][[1]]) %>% filter(time %in% c(150:270)) %>%
    group_by(species) %>%
    left_join(., lf_census_prop[[s]]) %>%
    #group_map(~ plotlen(.x), keep = TRUE)
    group_map(~ plotlen(.x, effN = 10000, truedat = 1), keep = TRUE) # plots merged true length comp

@@

#### Survey age composition (annual ages)
```{r plot-annagecomp-2, results="asis", message=FALSE, warning=FALSE}

@@

#### Survey iterpolated weight at age (annual ages) 
```{r plot-annwtage-2, fig.height=10, results='asis'}

@@

for(s in names(annage_wtage)){
  cat("  \n##### ",  s,"  \n")
  print(wageplot(annage_wtage[[s]][[1]]))
  cat("  \n")
}
```

@@

#diagnostic plot component still in this old version but just removed from function.
wageplot(fish_annage_wtage)
